Size Convergence of the E$\times$B \\ Staircase Pattern in Flux Tube \\ Simulations of Ion t Temperature \\ Gradient-Driven Turbulence

### 2023-06-21 presentation/presentation.tex
#39: ITG Turbulence picture redone

\title{Size convergence of the E$\times$B \\ Staircase pattern in flux tube \\ simulations of ion temperature \\ gradient driven turbulence}
\subtitle{~}
\author{Manuel Lippert}
\institute{Theoretical Physics V}

@@

		\begin{center}
			\begin{itemize}
				\item <2-> Ion temperature gradient driven turbulence close to marginal stability exhibits Zonal flow pattern formation on mesoscales 
				\item <3-> Patterns are called $\exb$ staircase structures
			\end{itemize}
		\end{center}
		\bigskip
		\onslide<4-> Observed pattern formation in
		\begin{center}
			\begin{itemize}
				\item <5-> local gradient-driven flux-tube simulations, including collisions and background $\exb$ shear,
				\item <6-> local flux-driven realizations, including mean electric field shear,
				\item <7-> global gradient-driven and global flux-driven studies.
			\end{itemize}
			\bigskip
			\onslide<8-> \textbf{Does the basic pattern size always converges to the box size, or is there a typical mesoscale size inherent to staircase structures also in a local flux-tube description?}
		\end{center}
	\end{frame}

@@

	\begin{frame}
		\frametitle{Ion Temperature Gradient (ITG) Driven Instability}
		\begin{center}
			\onslide<2->\input{../pictures/Theory/ITG-Turbulence.tex}
		\end{center}
	\end{frame}

@@

		\begin{minipage}{0.4\paperwidth}\raggedleft
			\begin{itemize}
				\item <2-> Parallel velocity $\Nvpar$ could be reduced from 64 to 48, which halfed the time until suppression of turbulence
				\item <3-> Restart Script with \texttt{python} led to further convenience during the task of performing simulations
				\item <4-> Mesoscale pattern size of $\sim 57 - 76\,\rhoth$ is found to be intrinsic to ITG driven turbulence for Cyclone Base Case parameters
				\item <5-> Finite heat flux threshold is located at $\rlt|_\mathrm{finite} = 6.3 \pm 0.1$
			\end{itemize}
		\end{minipage}
		\begin{minipage}{0.4\paperwidth}
			\onslide<4-> \includegraphics[width = 0.5\paperwidth]{Comparison/Boxsize/S6_rlt6.0_boxsize1-2-3-4x1-1.5-2-2.5-3-5_Ns16_Nvpar48_Nmu9_wexb_comparison_thesis.pdf}
		\end{minipage}
	\end{frame}

>>>>

\title{Size Convergence of the E$\times$B \\ Staircase Pattern in Flux Tube \\ Simulations of Ion t
Temperature \\ Gradient-Driven Turbulence}
\subtitle{~}
\author{Manuel Lippert}
\institute{Theoretical Physics V}

@@

		\begin{center}
			\begin{itemize}
				\item <2-> Ion temperature gradient-driven turbulence close to marginal stability exhibits Zonal flow pattern formation on mesoscales 
				\item <3-> Patterns are called $\exb$ staircase structures
			\end{itemize}
		\end{center}
		\bigskip
		\onslide<4-> Observed pattern formation in
		\begin{center}
			\begin{itemize}
				\item <5-> local gradient-driven flux-tube simulations, including collisions and background $\exb$ shear,
				\item <6-> local flux-driven realizations, including mean electric field shear,
				\item <7-> global gradient-driven and global flux-driven studies.
			\end{itemize}
			\bigskip
			\onslide<8-> \textbf{Does the basic pattern size always converges to the box size, or is there a typical mesoscale size inherent to staircase structures also in a local flux-tube description?}
		\end{center}
	\end{frame}

@@

	\begin{frame}
		\frametitle{Ion Temperature Gradient (ITG)-driven Instability}
		\begin{center}
			\onslide<2->\input{../pictures/Theory/ITG-Turbulence_Presentation.tex}
		\end{center}
	\end{frame}

@@

		\begin{minipage}{0.4\paperwidth}\raggedleft
			\begin{itemize}
				\item <2-> Parallel velocity $\Nvpar$ could be reduced from 64 to 48, which halfed the time until suppression of turbulence
				\item <3-> Restart Script with \texttt{python} led to further convenience during the task of performing simulations
				\item <4-> Mesoscale pattern size of $\sim 57 - 76\,\rhoth$ is found to be intrinsic to ITG-driven turbulence for Cyclone Base Case parameters
				\item <5-> Finite heat flux threshold is located at $\rlt|_\mathrm{finite} = 6.3 \pm 0.1$
			\end{itemize}
		\end{minipage}
		\begin{minipage}{0.4\paperwidth}
			\onslide<4-> \includegraphics[width = 0.5\paperwidth]{Comparison/Boxsize/S6_rlt6.0_boxsize1-2-3-4x1-1.5-2-2.5-3-5_Ns16_Nvpar48_Nmu9_wexb_comparison_thesis.pdf}
		\end{minipage}
	\end{frame}
